Karpov, Kasprov, Anand

### 2022-04-28 inst/kka.Rmd
white_draw3()

Draws would change this by introducing a weighted Draw monster D$:

@@

>>>>

Draws would change this by introducing a weighted Draw monster $D$:

@@

With strictly positive $D,D_1,D_2$ these are equal if and only if
$(\lambda-1)(p_1-p_2)=0$, that is, if the white advantage is
nonexistant, or if the players have the same strength.

We can use the bespoke function `white_draw3()` to make a likelihood
function:

```{r,makewhitedrawlike,cache=TRUE}
white_draw3(kka_array, 1.1, 2.3)
```

Then make a wrapper:

```{r,maxewhitedrawlike,cache=TRUE}
f <- function(v){
    lambda <- v[1]
    D      <- v[2]
    H <- white_draw3(kka_array, lambda,D)
    max(maxp(H,justlikes=TRUE))
}	
f(c(1.5,2.3))
```

```{r,contourlikewhite,cache=TRUE}
n <- 10
lambda <- seq(from=1.4,to=2.9,len=n)
D <- seq(from=1.6,to=3.4,len=n)	
M <- as.matrix(expand.grid(lambda=lambda,D=D))
l <- matrix(apply(M,1,f),n,n)
```

```{r}
l <- l-max(l)
contour(lambda,D,l,nlevels=30,xlab="lambda",ylab="D")
abline(v=lambda,col='gray',lwd=0.2)
abline(h=D,col='gray',lwd=0.2)
lambda
D
```
